Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-23 paper.qmd
Updated Figure 13

error_plot_pbmc <- ggplot(error_pbmc, 
                          aes(x = a1, 
                              y = log(MSE), 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a','#ff7f00',
                              '#984ea3','#999999','#a65628','#f781bf')) +
  ylab("log(MSE)") +
  xlab(expression(a[1])) + 
  theme(#aspect.ratio = 0.75,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7, angle = 90),
        axis.ticks.x = element_line(linewidth = 0.5),
        axis.ticks.y = element_line(linewidth = 0.5),
        legend.position = "none") #+
  # inset_element(p = pbmc_layouts, 
  #               left = 1.55, 
  #               bottom = 0.35, 
  #               right = 0, 
  #               top = 1)

>>>>

error_plot_pbmc <- ggplot(error_pbmc, 
                          aes(x = a1, 
                              y = log(MSE), 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a','#ff7f00',
                              '#984ea3','#999999','#a65628','#f781bf')) +
  ylab("log(MSE)") +
  xlab(expression(a[1])) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none")
